Misperceived Social Norms about Women Working Outside the Home and Its Effect on Women in Saudi Arabia

### 2024-02-12 outputs/paper/paper—copy.qmd

The authors calculated "wedges" which represent the difference between what participants guessed and the actual percentage of agreement among their session peers regarding women working outside the home (WWOH). The negative wedge indicates that the participant underestimated the support for WWOH. Conversely, a positive wedge suggests that the participant overestimated the support for WWOH. We replicate the histograms to check the distribution of the wedges between participants' beliefs about the support for WWOH among their session participants and the actual levels of support. @fig-1 specifically maps the distribution of these "wedges" – the differences between each participant's guess and the actual percentage of session participants who agreed with the pro-WWOH statement. It was found that more than half of participants underestimated the support for WWOH. There is a clear gap between perceived and actual social norms regarding women's work outside the home. The left skew of the histogram would indicate that a majority of participants underestimated the true level of support for WWOH.

@@

## Table 1 (Originally table 1)
```{r}
#| message: false
#| echo: false
# Read the dataset
main_clean <- read_dta(here("inputs/data/01_main_exp_clean_original.dta"))
follow_up_clean <- read_dta(here("inputs/data/02_follow_up_clean_original.dta"))
online_survey_clean <- read_dta(here("inputs/data/03_1st_online_svy_clean_original.dta"))
```

@@

table1 |> kbl(booktabs = T, col.names = c("All","Control","Treatment"), align=rep('c', 4)) |> 
  row_spec(1, hline_after = TRUE) |> kable_styling()
```
## Figure 2 (Originally figure 4)
```{r}
#| include: false
# Define path 
datadir <- "/cloud/project/inputs/data/"
data_path <- file.path(datadir, "clean_data/02_follow_up_clean.dta")

@@

```
By using the regression analysis, we examine the treatment effect on the participants' likelihood to sign up for a job matching service for their wives. The treatment variable is significant across all model specifications, with coefficients ranging from 0.0853 to 0.0899. The constant term varies considerably across different model specifications, suggesting differing baseline propensities for signing up absent the treatment. The p-values for the treatment effect, under various robustness checks such as robust standard errors, wild bootstrap, and permutation test, all indicate significance, ranging from 0.008 to 0.038. These results reinforcing the treatment's positive impact on sign-up rates @tbl-summary_table.

## Figure 2 original fig 3
Fig-2 illustrates the difference in job matching service sign-up rates between the control and treatment groups. The bar for the treatment group would be higher than the control group's, showing a clear increase in the likelihood of signing up due to the treatment. The specific values of 23.48% for the control group and 32.02% for the treatment group, along with a p-value of 0.017, would be represented, indicating a statistically significant effect of the information intervention on the participants' actions.

@@

## Figure 3 (Originally figure 6)
```{r}
#| message: false
#| echo: false
outside_value <- na.omit(online_survey_clean$c_outside_guess_frac)
group <- rep("Control", length(outside_value))
c_outside <- cbind(outside_value, group)
c_outside <- data.frame(c_outside)

@@

# Appendix {-}

>>>>

The authors calculated "wedges" which represent the difference between what participants guessed and the actual percentage of agreement among their session peers regarding women working outside the home (WWOH). The negative wedge indicates that the participant underestimated the support for WWOH. Conversely, a positive wedge suggests that the participant overestimated the support for WWOH. We replicate the histograms to check the distribution of the wedges between participants' beliefs about the support for WWOH among their session participants and the actual levels of support. @fig-1 specifically maps the distribution of these "wedges" -- the differences between each participant's guess and the actual percentage of session participants who agreed with the pro-WWOH statement. It was found that more than half of participants underestimated the support for WWOH. There is a clear gap between perceived and actual social norms regarding women's work outside the home. The left skew of the histogram would indicate that a majority of participants underestimated the true level of support for WWOH.

@@

### Table 1 (Originally table 1)

```{r}
#| message: false
#| echo: false
# Read the dataset
main_clean <- read_dta(here("inputs/data/01_main_exp_clean_original.dta"))
follow_up_clean <- read_dta(here("inputs/data/02_follow_up_clean_original.dta"))
online_survey_clean <- read_dta(here("inputs/data/03_1st_online_svy_clean_original.dta"))
```

## Figure 1 (Originally figure 2)

## Figure 2 (Originally figure 3)

```{r}
#| message: false
#| echo: false
p_value_figure3 <- chisq.test(table(main_clean$condition2, main_clean$signed_up_number))

percentage_data_figure3 <- main_clean |>
  mutate(condition2 = ifelse(condition2 == 0, 'Control', 'Treatment')) |>
  group_by(condition2) |>
  summarise(percentage = mean(signed_up_number == 1) * 100)
```

```{r}
#| message: false
#| echo: false
#| label: fig-job_sign_up
#| fig-cap: Job Matching Service Sign Up (Main Experiment)
plot_figure3 <- ggplot(percentage_data_figure3, aes(x = condition2, y = percentage)) +
  geom_bar(stat = "identity", fill = "grey", color = "black", alpha = 0.9) +
  labs(x = "",
       y = "Percent sign up") +
  geom_text(aes(label = paste0(round(percentage, 2), "%")),
            position = position_dodge(width = 0.9),
            vjust = -0.5) +
  annotate("text", x = 1.5, y = 37, label = sprintf("p-value = %.4f", p_value_figure3$p.value)) +
  theme_minimal() + 
  ylim(0, 40)

plot_figure3
```

## Table 1 (Originally table 1)

@@

table1 |> kbl(booktabs = T, col.names = c("All","Control","Treatment"), align=rep('c', 4)) |> 
  row_spec(1, hline_after = TRUE) |> kable_styling()
```

## Figure 2 (Originally figure 4)

```{r}
#| include: false
# Define path 
datadir <- "/cloud/project/inputs/data/"
data_path <- file.path(datadir, "clean_data/02_follow_up_clean.dta")

@@

By using the regression analysis, we examine the treatment effect on the participants' likelihood to sign up for a job matching service for their wives. The treatment variable is significant across all model specifications, with coefficients ranging from 0.0853 to 0.0899. The constant term varies considerably across different model specifications, suggesting differing baseline propensities for signing up absent the treatment. The p-values for the treatment effect, under various robustness checks such as robust standard errors, wild bootstrap, and permutation test, all indicate significance, ranging from 0.008 to 0.038. These results reinforcing the treatment's positive impact on sign-up rates @tbl-summary_table.

## Figure 2 original fig 3

Fig-2 illustrates the difference in job matching service sign-up rates between the control and treatment groups. The bar for the treatment group would be higher than the control group's, showing a clear increase in the likelihood of signing up due to the treatment. The specific values of 23.48% for the control group and 32.02% for the treatment group, along with a p-value of 0.017, would be represented, indicating a statistically significant effect of the information intervention on the participants' actions.

@@

## Figure 3 (Originally figure 6)

```{r}
#| message: false
#| echo: false
outside_value <- na.omit(online_survey_clean$c_outside_guess_frac)
group <- rep("Control", length(outside_value))
c_outside <- cbind(outside_value, group)
c_outside <- data.frame(c_outside)

@@

# Appendix {.unnumbered}
